Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-05-13 Latex/sections/simulation.tex
Added Info about the Livox Scanners

For the simulated data, we implemented a noisy world-robot-sensor model.  
We are simulating a LIVOX-Mid100~\cite{LivoxMid40-100} laser scanner with customizable noise level on the range measurements inside a robot with different motion capabilities, subject to noise in its pose estimation. This yields scan results similar to the ones obtained in the real world.

>>>>

For the simulated data, we implemented a noisy world-robot-sensor model.  
We are simulating a Livox-Mid100~\cite{LivoxMid40-100} laser scanner with customizable noise level on the range measurements inside a robot with different motion capabilities, subject to noise in its pose estimation. 
This yields scan results similar to the ones obtained in the real world.

\subsection{Simulated Sensor}

The Livox-Mid100 laser scanner consists of three smaller-sized Mid40 scanners arranged to provide an overall field-of-view of \SI{98.4}{\degree} (Horizontal) by \SI{38.4}{\degree} (Vertical).
It provides a range precision of \SI{2}{\centi\meter} up to \SI{20}{\meter} range and yields \SI[per-mode=symbol]{300,000}{\pts\per\second}.
A particular advantage of the Livox laser scanners is their unique scanning pattern.
The scanners use two motorized, so-called Risley prisms to steer the beam deflectance.
For the specific ratio of rotation speeds used in the Livox scanners, the beam traces out a non-repetitive, flower-shaped scanning pattern~\cite{thorlabs}.
Since the pattern is non-repetitive, the point density increases with integration time, enabling denser measurements.
